Time Series Bootstrapping For Solar Current

### 2021-12-14 deliverables/paper.Rmd
Added initial methods section with bootstrapping algorithm and justification

# Bootstrapping

@@

>>>>

# Methods

@@

The main goal of this paper is to provide point and interval
estimates for average (simulated) current output
based on solar irradiance.
Given that the sample size is large,
a simple average may have been sufficient.
However, we were interested in characterizing
the difference in performance between
standard bootstrapping methods and dependent bootstrapping methods.
The current output provides a good test case for this.
Both the preprocessed and postprocessed currents are not independent data;
values of either irradiance or current output
depend on surrounding values in time.
As such, standard methods for bootstrapping should be
less effective at estimating the true mean irradiance output.

The standard (*iid*) bootstrap procedure begins with
the assumption that our original sample consists of
independent and identically distributed draws from a distribution.
The univariate bootstrap then provides a distribution of bootstrap
estimates for a statistic,
$\hat{\theta}^{(1)}, \ldots, \{\hat{\theta}^{(B)}$,
where $B$ is the number of bootstrap replicates
and $\theta$ is a statistic of interest.
For our purposes, $\theta$ is simply the average current output
for our specific solar module configuration.
The *iid* bootstrap constructs the distribution of bootstrap estimates
as follows:

For $i = 1, \ldots, B$:

1. Sample $n$ values $x_j$ from the data with replacement
1. Calculate
   $\hat{\theta}^{(i)} = \frac{1}{n} \sum_{j = 1}^{n} x_j$
   for the bootstrap sample.

In contrast, a dependent bootstrap does not assume
the original sample was independent and identically distributed.
To capture the dependence in the data,
we chose to use a nonparametric non-overlapping block bootstrap.
This is because during the data filtering step,
we excluded nighttime values from the dataset.
This meant we essentially had predefined,
mostly independent blocks from which to sample:
the daytime current values for each day.
Given that our daytime current values for each day
could be used as non-overlapping blocks,
our dataset could be seen as a collection
of $n_B$ blocks.

For i = $1, \ldots, B$:

1. Sample $n_B$ blocks (days)
$\mathcal{B}_{1}, ..., \mathcal{B}_{n_B}$
from the data with replacement.
1. Calculate
   $\hat{\theta}^{(i)} = \frac{1}{n} \sum_{j = 1}^{n} x_j$
   on a new dataset
  $\mathcal{B}_{1} \cup \cdots \cup \mathcal{B}_{n_B}$.

The new dataset in Step 2
corresponds to sampling and rearranging days to make
a new dataset the same size as the original.
This procedure preserves the dependence within days,
while still allowing resampling.

# Results
